\documentclass[a4paper, 12pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[dvips, bookmarks, bookmarksnumbered, colorlinks=false, linkbordercolor={1 1 1}]{hyperref}

\hypersetup{
	pdfauthor = {flexworld-game.com},
	pdftitle = {Testing Team Guide},
	pdfsubject = {Testing Team Guide},
	pdfcreator = {LaTeX with hyperref package},
}

\parskip 12pt
\parindent 0pt

\title{Testing Team Guide}
\author{flexworld-game.com}

\begin{document}

\maketitle
\tableofcontents

\section{About this document}

This document gives some brief information about workflows, requirements and
account info for FlexWorld testing team members.

\section{Tasks and requirements}

The testing team's tasks are:

\begin{itemize}
	\item Ensuring FlexWorld runs on each target platform.
	\item Checking that new features and bugfixes are working properly.
	\item Reporting bugs at the Redmine bug tracker.
	\item Reporting ideas/wishes for new features.
	\item Giving appropriate feedback to release mails as requested.
	\item Actively taking part on the mailing list/in discussions.
\end{itemize}

Please be aware that being a tester does \textbf{not} mean to only get access to
regular testing releases and play around. Instead you play an important role in
the development process.

It's required to give appropriate feedback, whether if it's explicitely
requested or not. That also includes taking part in discussions on the mailing
list aswell as on Redmine by commenting on tickets (primarily confirming that a
bug also happens on your system, or by commenting on ideas of others).

In case you don't have enough time or aren't interested anymore please be honest
and talk to us.

\textbf{Users who don't actively take part will be sooner or later dropped from the
team.}

\section{Tools and Accounts}

Development of FlexWorld is organized in several tools. Collecting ideas and bug
reports happens mostly in \textit{Redmine}, a web-based bug and task tracker.
General discussions also take place there, but also on the mailing list.

\subsection{Redmine}

The Redmine instance can be accessed at \url{http://redmine.boxbox.org}. Please
register an account there and send a mail to the project maintainer containing
your username. You will then be added to the proper groups to get access.

FlexWorld is organized in sub-projects. The parent project is called
\textit{FlexWorld (Scrum)}. The sub-projects that are interesting for testers
are:

\begin{itemize}
	\item \textbf{Ideas:} Collecting and discussing new ideas/feature requests.
	\item \textbf{Testing:} Reporting and discussing bug reports/problems.
\end{itemize}

Just click on \textit{Projects} at the top to get to the proper projects.

Before you create a new ticket (called \textit{issues} in Redmine), make sure
the same idea/bug hasn't been reported yet.

Each project also contains a Wiki with additional and important information.
Make sure you read it!

\subsection{Sprint releases}

FlexWorld follows the \textit{Scrum workflow} and our sprint interval is set to
one week. That means if nothing bad happens, a sprint release is made every
week, mostly either on Saturday or Sunday.

You can find the packaged files in the \textit{Testing} project in Redmine.
Click on \textit{Files} in the menu.

\subsection{Mailing list}

General communication and announcing new sprint releases (often together with
request for feedback) happens on the \textit{fw-test mailing list}. Each testing
team member has a subscription to it and can therefore be reached there.

Keep in mind that sending an e-mail to the mailing list will be delivered to
\textbf{all} members. If you want to reach a single member, check the wiki page
at the testing project.

When feedback is requested for sprint releases, always reply to the list, so
that all testers can read it.

The address of the mailing list is \texttt{fw-test@boxbox.org}.

\subsection{IRC}

For more interactive and faster communications you can join FlexWorld's IRC
channel. Connect your IRC client to \texttt{irc.boxbox.org}, port 6667 or 6697
(SSL-enabled), channel \texttt{\#flexworld}.

\subsection{FTP}

To exchange files there exists an FTP site for testing team members. It can be
reached at \texttt{boxbox.org}, port 21.

For username and password information please contact the project maintainer.

\section{Creating content}

As a tester you mostly have access to the newest bleeding-edge features. We
highly encourage every tester to \textit{play around with them}, e.g.

\begin{itemize}
	\item writing Lua scripts,
	\item creating and importing 3D models,
	\item adding/modifying textures,
	\item building landscapes, buildings etc.
	\item creating screenshots
\end{itemize}

and many more.

If you created anything interesting, feel free to upload it to the FTP site.

\section{Reward}

As soon as FlexWorld is sold, every single person contributing to the project
will be paid.

The amount of the reward depends on several factors and we'd like to talk to
each of you to discuss yours.

Please \textbf{do not} take part in FlexWorld development if you can't accept
that fact. We perfectly understand that working for the project without getting
something in return in the beginning might be demotivating.

Just talk to us if there's anything unclear in that regard.

\section{Contact}

\subsection{Developers}

\begin{itemize}
	\item Stefan »Tank« Schindler \texttt{<stefan@flexworld-game.com>}
\end{itemize}

\subsection{Web developers}

\begin{itemize}
	\item Sven »resident-uhlig« Uhlig \texttt{<sven@flexworld-game.com>}
\end{itemize}

\subsection{Testing team}

The testing team is coordinated by Lukas (\textit{eXpl0it3r})
\texttt{<lukas@flexworld-game.com>}. If you have any questions or comments,
feel free to contact him.

For a full list of all members see
\footnote{\url{http://redmine.boxbox.org/projects/fw-main-testing/wiki/Testing\_team\_members}}.

\section{Conclusion}

Thanks for taking part in the development process of FlexWorld. It's highly
appreciated and we'd like to tell all of you that all your work is very valuable
for the whole project.

If you have any questions, feedback or criticism, please contact the project
maintainer or the testing team coordinator.

\end{document}
